Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-07-11 thirdPaper/draft/typeConeAssociahedra.tex
corollaire uerp gentle

Let~$\quiver = (Q,I)$ be a gentle bound quiver, and let~$\Fan(\quiver)$ be the fan of its~$\b{g}$-vectors (\cref{subsubsec:nonkissingComplex}), also called its non-kissing fan.
We prove in \cref{sect::Kbproj}, by making use of representation theory:

@@

\noindent \cref{prop:exchangeablePairsNKC} (ii): \emph{The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.}
\arnau{In the proof of \cref{prop:exchangeablePairsNKC} it says that the UERP follows from PPP17}\pg{Not for point (ii), which uses results of Section 4}
\medskip

@@

\item For any non-kissing facets~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, the distinguished substrings of~$\omega$ in~$F$ and of~$\omega'$ in~$F'$ coincide to a string~$\sigma$. Moreover, if we decompose~${\omega = \rho \sigma \tau}$ and~${\omega' = \rho' \sigma \tau'}$, then the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ only depend on the exchangeable walks~$\omega$ and~$\omega'$, and not on the adjacent non-kissing facet~$F $ and~$F'$.
\item The linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
\[
\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}.
\]
In other words, the non-kissing fan of~$\quiver$ has the unique exchange relation property.
\item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\lambda}$ for~$\lambda \in F \cap F'$ is the multiplicity vector~$\multiplicityVector_{\sigma}$ of the vertices of the substring~$\sigma$ of~$\omega$ and~$\omega'$.
\end{enumerate}
%
\begin{figure}[b]
	\capstart
	\centerline{\includegraphics[scale=1]{flip}}
	\caption{A schematic representation of a flip. Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
	\label{fig:flip}
\end{figure}
\end{proposition}

@@

>>>>

Let~$\quiver = (Q,I)$ be a gentle bound quiver, and let~$\Fan(\quiver)$ be the fan of its~$\b{g}$-vectors (\cref{subsubsec:nonkissingComplex}), also called its non-kissing fan.
We prove \cref{prop:exchangeablePairsNKC} (ii) in \cref{sect::Kbproj}, by making use of representation theory, and state here the following consequence:

@@

\noindent \cref{corollary: uerp gentle}: \emph{The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.}
\arnau{In the proof of \cref{prop:exchangeablePairsNKC} it says that the UERP follows from PPP17}\pg{Not for point (ii), which uses results of Section 4}
\medskip

@@

\item For any non-kissing facets~$F, F'$ of~$\NKC$ with~$F \ssm \{\omega\} = f' \ssm \{\omega'\}$, the distinguished substrings of~$\omega$ in~$F$ and of~$\omega'$ in~$F'$ coincide to a string~$\sigma$. Moreover, if we decompose~${\omega = \rho \sigma \tau}$ and~${\omega' = \rho' \sigma \tau'}$, then the facets~$F$ and~$F'$ both contain the walks~$\mu \eqdef \rho' \sigma \tau$ and~$\nu \eqdef \rho \sigma \tau'$.
\item The substring~$\sigma$ and thus the walks~$\mu$ and~$\nu$ only depend on the exchangeable walks~$\omega$ and~$\omega'$, and not on the adjacent non-kissing facet~$F $ and~$F'$.
\item The linear dependence between the $\b{g}$-vectors of~$F \cup F'$ is given by
\[
\gvector{\omega} + \gvector{\omega'} = \gvector{\mu} + \gvector{\nu}.
\]
% In other words, the non-kissing fan of~$\quiver$ has the unique exchange relation property.
\item The $\b{c}$-vector orthogonal to all $\b{g}$-vectors~$\gvector{\lambda}$ for~$\lambda \in F \cap F'$ is the multiplicity vector~$\multiplicityVector_{\sigma}$ of the vertices of the substring~$\sigma$ of~$\omega$ and~$\omega'$.
\end{enumerate}
%

@@

As a consequence of points $(ii)$ and $(iii)$ in \cref{prop:exchangeablePairsNKC}, we obtain the:
\begin{corollary}
\label{corollary: uerp gentle}
For any non-kissing finite gentle bound quiver~$\quiver$, the non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.
\end{corollary}

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{flip}}
	\caption{A schematic representation of a flip. Illustration from~\cite{PaluPilaudPlamondon-nonkissing}.}
	\label{fig:flip}
\end{figure}
\end{proposition}
